Motivating Exploration in Reinforcement Learning

### 2020-04-17 paper/main.tex
Update main.tex
update figures

In this work, we explore a general formulation of curiosity that aims to motivate exploration in reinforcement learning (RL) agents while remaining invariant to the algorithm and task in question. We explore the effects of including an entropy term (of the policy action probability distribution) and a curiosity module based on that of \cite{curiosity}, which provides an intrinsic reward signal. Due to the scope of the porject, we focus specifically on the Advantage Actor-Critic (A2C) RL algorithm in the \textit{Pong}, \textit{Seaquest}, and \textit{Breakout} Atari environments. These tasks were chosen due to the differences in mechanics and their respective state spaces, specifically the density and magnitude of the extrinsic reward (i.e. reward received from environment itself).

We compare the performance of the agent in the various environments with and without the mentioned exploration factors. \textbf{Add more on the experimental results once that's finalized}

@@

\subsubsection{Dense Extrinsic Reward}
\begin{figure}
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=1.\linewidth]{figures/pong_rewards}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=1.\linewidth]{figures/pong_rewards}
\end{subfigure}
\caption{Here we compare the three A2C variants in the \texttt{Breakout} (left) and \texttt{Seaquest} (right) environments. Rewards are again cumulative over an entire episode.}
\label{fig:seaquest-breakout-reward}
\end{figure}

>>>>

In this work, we explore a general formulation of curiosity that aims to motivate exploration in reinforcement learning (RL) agents while remaining invariant to the algorithm and task in question. We explore the effects of including an entropy term (of the policy action probability distribution) and a curiosity module based on that of \cite{curiosity}, which provides an intrinsic reward signal. Due to the scope of the porject, we focus specifically on the Advantage Actor-Critic (A2C) RL algorithm in the \textit{Pong}, \textit{Seaquest}, and \textit{Breakout} Atari environments. These tasks were chosen due to the differences in mechanics and their respective state spaces, specifically the density and magnitude of the extrinsic reward (i.e. reward received from environment itself). Moreover, our general formulation of curiosity through an entropy term and a curiosity module have not been applied to these specific environments previously.

We compare the performance of the agent in the various environments with and without the mentioned exploration factors. We expected to see better performance in sparse environments with the ICM module, but with regards to denser environments, we expected to see a mitigated effect from the ICM module compared to the sparse environments.

@@

\subsubsection{Dense Extrinsic Reward}
\begin{figure}
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=1.\linewidth]{figures/breakout_rewards}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=1.\linewidth]{figures/seaquest_rewards}
\end{subfigure}
\caption{Here we compare the three A2C variants in the \texttt{Breakout} (left) and \texttt{Seaquest} (right) environments. Rewards are again cumulative over an entire episode.}
\label{fig:seaquest-breakout-reward}
\end{figure}
